---
title: "Gov 94OA Analysis"
author: "Monica Chang"
date: "5/6/2021"
output: 
  pdf_document:
    extra_dependencies: ["dcolumn"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(janitor)
library(rstanarm)
library(stargazer)
library(haven)
library(modEvA)
library(dplyr)
library(statxp)
library(gt)
library(cowplot)
library(kableExtra)
library(splitstackshape)
library(readxl)
```

## imputing percentages with Gilens' data

```{r impute gilens data, warning = FALSE}
clean_gilens <- read_csv(file = "clean_data/clean_gilens.csv")

clean_gilens_2 <- clean_gilens %>%
  dplyr::select(id8102, year, outcome, switcher, xl_area, inc1_fav:inc12_dk) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  rowwise() %>% 
  
  # I add columns to specify the number of respondents in each income group
  # and the number of total survey respondents for each question.
  
  mutate(inc1 = sum(inc1_fav, inc1_opp, inc1_dk, na.rm = TRUE),
         inc2 = sum(inc2_fav, inc2_opp, inc2_dk, na.rm = TRUE),
         inc3 = sum(inc3_fav, inc3_opp, inc3_dk, na.rm = TRUE),
         inc4 = sum(inc4_fav, inc4_opp, inc4_dk, na.rm = TRUE),
         inc5 = sum(inc5_fav, inc5_opp, inc5_dk, na.rm = TRUE),
         inc6 = sum(inc6_fav, inc6_opp, inc6_dk, na.rm = TRUE),
         inc7 = sum(inc7_fav, inc7_opp, inc7_dk, na.rm = TRUE),
         inc8 = sum(inc8_fav, inc8_opp, inc8_dk, na.rm = TRUE),
         inc9 = sum(inc9_fav, inc9_opp, inc9_dk, na.rm = TRUE),
         inc10 = sum(inc10_fav, inc10_opp, inc10_dk, na.rm = TRUE),
         inc11 = sum(inc11_fav, inc11_opp, inc11_dk, na.rm = TRUE),
         inc12 = sum(inc12_fav, inc12_opp, inc12_dk, na.rm = TRUE),
         total = sum(inc1_fav, inc2_fav, inc3_fav, inc4_fav, inc5_fav, inc6_fav,
                     inc7_fav, inc8_fav, inc9_fav, inc10_fav, inc11_fav, inc12_fav,
                     inc1_opp, inc2_opp, inc3_opp, inc4_opp, inc5_opp, inc6_opp,
                     inc7_opp, inc8_opp, inc9_opp, inc10_opp, inc11_opp, inc12_opp,
                     inc1_dk, inc2_dk, inc3_dk, inc4_dk, inc5_dk, inc6_dk,
                     inc7_dk, inc8_dk, inc9_dk, inc10_dk, inc11_dk, inc12_dk, 
                     na.rm = TRUE)) %>%

  # I add columns to contain the income percentile scores for each income 
  # group.
  
  mutate(inc1_score = (inc1/total)/2,
         inc2_score = inc1_score + (inc1/total)/2 + (inc2/total)/2,
         inc3_score = inc2_score + (inc2/total)/2 + (inc3/total)/2,
         inc4_score = inc3_score + (inc3/total)/2 + (inc4/total)/2,
         inc5_score = inc4_score + (inc4/total)/2 + (inc5/total)/2,
         inc6_score = inc5_score + (inc5/total)/2 + (inc6/total)/2,
         inc7_score = inc6_score + (inc6/total)/2 + (inc7/total)/2,
         inc8_score = inc7_score + (inc7/total)/2 + (inc8/total)/2,
         inc9_score = inc8_score + (inc8/total)/2 + (inc9/total)/2,
         inc10_score = inc9_score + (inc9/total)/2 + (inc10/total)/2,
         inc11_score = inc10_score + (inc10/total)/2 + (inc11/total)/2,
         inc12_score = inc11_score + (inc11/total)/2 + (inc12/total)/2)


impute_preferences <- function(df){
  
  df <- df %>%
    
    # I initialize columns to save the coefficients of the logistic regression
    # and the imputed percentages of 50th percentile and 90th percentile 
    # voters in favor of policy change.
    
    mutate(coef_intercept = 0) %>%
    mutate(coef_income = 0) %>%
    mutate(coef_income_squared = 0) %>%
    mutate(pred50_sw = 0) %>%
    mutate(pred90_sw = 0)
  
  # I loop through each row (survey question) of the dataframe.
  
  for(i in 1:nrow(df)){
  
    # For each row, I create a tibble with preference, income, and income^2 columns.
    # I am re-constituting the individual level data for each survey question.
    
    question_data <- tibble(preference = numeric(), income = numeric(), income_sq = numeric())
     
      # For each income/preference category (e.g. inc1_fav), I do the following:
    
      for(j in 6:41){
       
         # I initialize an empty tibble to contain information for the survey 
         # respondents in this income preference category.
         
         inc_group_data <- tibble(preference = numeric(), 
                                  income = numeric(), 
                                  income_sq = numeric())
         
         # I store the number of individuals in that income/preference category.
        
         x <- ifelse(!is.na(df[i,][j][[1]]), df[i,][j][[1]], 0)
         
         # I store the appropriate income score for the income/preference category.
         
         score <- ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc1", df[i,]$inc1_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc2", df[i,]$inc2_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc3", df[i,]$inc3_score,
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc4", df[i,]$inc4_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc5", df[i,]$inc5_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc6", df[i,]$inc6_score,
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc7", df[i,]$inc7_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc8", df[i,]$inc8_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc9", df[i,]$inc9_score,
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc10", df[i,]$inc10_score, 
                  ifelse(substr(colnames(df[i,][j]), 1, 4) == "inc11", df[i,]$inc11_score, 
                          df[i,]$inc12_score)))))))))))
                          
         # I store the appropriate preference number for the income/preference 
         # category. 1 indicates "favor," 0 indicates "oppose," and NA indicates
         # "don't know."
         
         pref <- ifelse(substr(colnames(df[i,][j]), 6, 8) == "fav", 1, 
                               ifelse(substr(colnames(df[i,][j]), 6, 8) == "opp",
                                       0, NA))
        
         # I add x number of rows to tibble y to reflect the x individuals in
         # this income/preference category for this survey question.
         
         inc_group_data <- inc_group_data %>% 
           add_row(preference = pref, income = score, income_sq = score*score)
             
         inc_group_data <- expandRows(inc_group_data, count=x, count.is.col=FALSE)
        
         question_data <- rbind(question_data, inc_group_data)
         
     } 
    
     # After adding rows for each individual that took the survey to the 
     # tibble, we can run a logistic regression.
      
     model <- glm(preference ~ income + income_sq, 
                  family = binomial(link = "logit"),
                  data = question_data)
      
    # I save the regression coefficients to the row for easy use in 
    # imputing the percent favor of other percentiles.
    
    df[i,]$coef_intercept <- coef(model)[[1]]
    df[i,]$coef_income <- coef(model)[[2]]
    df[i,]$coef_income_squared <- coef(model)[[3]]
    
    # I calculate the imputed percentage of median voters and 90th percentile
    # voters that would favor a proposed policy change.
    
    df[i,]$pred50_sw <- invlogit(coef(model)[[1]] + coef(model)[[2]]*0.5 + coef(model)[[3]]*0.5*0.5)
    df[i,]$pred90_sw <- invlogit(coef(model)[[1]] + coef(model)[[2]]*0.9 + coef(model)[[3]]*0.9*0.9)
    
    # If the survey response of “favor” reflects a preference for the status 
    # quo, I invert the favor and oppose measures.
    
    if(df[i,]$switcher == 1){
      df[i,]$pred50_sw <- 1 - df[i,]$pred50_sw
      df[i,]$pred90_sw <- 1 - df[i,]$pred90_sw
    }
  }
  
  return(df)
}

# clean_gilens_3 <- impute_preferences(clean_gilens_2)

# write_csv(clean_gilens_3, file = "clean_data/clean_gilens_imputed")

# Compare how close my imputation is to Gilens' imputation.

# a <- clean_gilens %>% 
#   dplyr::select(id8102, pred50_sw, pred90_sw)
# b <- clean_gilens_3 %>% 
#  dplyr::select(id8102, pred50_sw, pred90_sw) %>%
#  rename(id8102_2 = id8102, pred50_sw_2 = pred50_sw, pred90_sw_2 = pred90_sw)
# c <- cbind(a, b) %>% 
#  mutate(diff_50 = pred50_sw_2 - pred50_sw, diff_90 = pred90_sw_2 - pred90_sw)
```
    
## Imputing percentages with my own data

```{r add income percentile scores to my data, warning = FALSE}
new_data <- read_excel(path = "clean_data/new_data.xlsx") %>%
  clean_names() %>%
  mutate(id = 1:152) 

new_data_2 <- new_data %>% 
  dplyr::select(id, year, outcome, switcher, xl_area, inc1_fav:inc12_dk, budget_reconciliation, filibuster_proof) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  rowwise() %>% 
  
  # I add columns to specify the number of respondents in each income group
  # and the number of total survey respondents for each question.
  
  mutate(inc1 = sum(inc1_fav, inc1_opp, inc1_dk, na.rm = TRUE),
         inc2 = sum(inc2_fav, inc2_opp, inc2_dk, na.rm = TRUE),
         inc3 = sum(inc3_fav, inc3_opp, inc3_dk, na.rm = TRUE),
         inc4 = sum(inc4_fav, inc4_opp, inc4_dk, na.rm = TRUE),
         inc5 = sum(inc5_fav, inc5_opp, inc5_dk, na.rm = TRUE),
         inc6 = sum(inc6_fav, inc6_opp, inc6_dk, na.rm = TRUE),
         inc7 = sum(inc7_fav, inc7_opp, inc7_dk, na.rm = TRUE),
         inc8 = sum(inc8_fav, inc8_opp, inc8_dk, na.rm = TRUE),
         inc9 = sum(inc9_fav, inc9_opp, inc9_dk, na.rm = TRUE),
         inc10 = sum(inc10_fav, inc10_opp, inc10_dk, na.rm = TRUE),
         inc11 = sum(inc11_fav, inc11_opp, inc11_dk, na.rm = TRUE),
         inc12 = sum(inc12_fav, inc12_opp, inc12_dk, na.rm = TRUE),
         total = sum(inc1_fav, inc2_fav, inc3_fav, inc4_fav, inc5_fav, inc6_fav,
                     inc7_fav, inc8_fav, inc9_fav, inc10_fav, inc11_fav, inc12_fav,
                     inc1_opp, inc2_opp, inc3_opp, inc4_opp, inc5_opp, inc6_opp,
                     inc7_opp, inc8_opp, inc9_opp, inc10_opp, inc11_opp, inc12_opp,
                     inc1_dk, inc2_dk, inc3_dk, inc4_dk, inc5_dk, inc6_dk,
                     inc7_dk, inc8_dk, inc9_dk, inc10_dk, inc11_dk, inc12_dk, 
                     na.rm = TRUE)) %>%

  # I add columns to contain the income percentile scores for each income 
  # group.
  
  mutate(inc1_score = (inc1/total)/2,
         inc2_score = inc1_score + (inc1/total)/2 + (inc2/total)/2,
         inc3_score = inc2_score + (inc2/total)/2 + (inc3/total)/2,
         inc4_score = inc3_score + (inc3/total)/2 + (inc4/total)/2,
         inc5_score = inc4_score + (inc4/total)/2 + (inc5/total)/2,
         inc6_score = inc5_score + (inc5/total)/2 + (inc6/total)/2,
         inc7_score = inc6_score + (inc6/total)/2 + (inc7/total)/2,
         inc8_score = inc7_score + (inc7/total)/2 + (inc8/total)/2,
         inc9_score = inc8_score + (inc8/total)/2 + (inc9/total)/2,
         inc10_score = inc9_score + (inc9/total)/2 + (inc10/total)/2,
         inc11_score = inc10_score + (inc10/total)/2 + (inc11/total)/2,
         inc12_score = inc11_score + (inc11/total)/2 + (inc12/total)/2)
```

```{r calculating gridlock and seat advantage, warning = FALSE}
a <- new_data %>%
  group_by(year) %>%
  summarize(proposed_changes = n())

b <- new_data %>%
  filter(outcome == 1) %>%
  group_by(year) %>%
  summarize(adopted_changes = n())

c <- inner_join(a, b) %>%
  mutate(gridlock = ((proposed_changes - adopted_changes)/proposed_changes)*100)

d <- c %>% select(year, gridlock)

ggplot(c, aes(x = year, y = gridlock)) +
  
  # There were only one time period during the 111th Congress when the Democrats 
  # had a 60 seat majority:
  
  # From September 25, 2009 (when Paul Kirk was appointed to replace Kennedy) 
  # to February 4, 2010 (when Scott Brown took office after defeating Martha 
  # Coakley);
  
  geom_rect(aes(xmin = 2009.731, xmax = 2010.093, ymin = -Inf, ymax = Inf), alpha = 0.1, fill = "red") +
  geom_line() +
  labs(title = "Change in gridlock from 2009-2013",
       subtitle = "Red area indicates the 4-month time period in which the Senate Democrats \nhad a filibuster-proof majority. Gridlock is measures as the percentage of \nproposed policy changes not adopted.",
       x = "Year",
       y = "Gridlock") +
  theme_linedraw() +
  geom_vline(xintercept = 2009.731, lty = "dashed", color = "red") +
  geom_vline(xintercept = 2010.093, lty = "dashed", color = "red") +
  ylim(0, 100)

senate <- tibble(year = c(2009, 2010, 2011, 2012, 2013),
                 sen_dems = c(59, 59, 53, 53, 55),
                 sen_reps = c(41, 41, 47, 47, 45),
                 sen_majority = c("D", "D", "D", "D", "D")) %>%
  mutate(sen_seat_advantage = sen_dems - sen_reps)

ggplot(senate, aes(x = year, y = sen_seat_advantage)) +
  geom_rect(aes(xmin = 2009.731, xmax = 2010.093, ymin = -Inf, ymax = Inf), alpha = 0.1, fill = "red") +
  geom_line() +
  labs(title = "Change in Senate Democrats' seat advantage from 2009-2013",
       subtitle = "Red area indicates the 4-month time period in which the Democrats \n had a filibuster-proof majority.",
       x = "Year",
       y = "Senate Democrats' seat advantage") +
  theme_linedraw() +
  geom_vline(xintercept = 2009.731, lty = "dashed", color = "red") +
  geom_vline(xintercept = 2010.093, lty = "dashed", color = "red") +
  ylim(0, 20)


house <- tibble(year = c(2009, 2010, 2011, 2012, 2013),
                 hs_dems = c(256, 256, 193, 193, 200),
                 hs_reps = c(178, 178, 242, 242, 233),
                 hs_majority = c("D", "D", "R", "R", "R")) %>%
  mutate(hs_seat_advantage = hs_dems - hs_reps)

ggplot(house, aes(x = year, y = hs_seat_advantage)) +
  geom_line() +
  labs(title = "Change in House Democrats' seat advantage from 2009-2013",
       x = "Year",
       y = " House Democrats' seat advantage") +
  theme_linedraw() +
  geom_hline(yintercept = 0, lty = "dashed")

cloture <- tibble(year = c(2009, 2010, 2011, 2012, 2013),
                  cloture = c(69, 68, 48, 67, 78))

e <- inner_join(d, inner_join(cloture, inner_join(house, senate))) %>%
  mutate(unified = if_else(sen_majority == "D" & hs_majority == "D", 1, 0)) %>%
  select(year, gridlock, sen_seat_advantage, hs_seat_advantage, unified, cloture) 

new_data_predictors <- inner_join(new_data_2, e)
```

$$ policy\_preference = \beta_0*income + \beta_1*income^2 $$

```{r impute my data, warning = FALSE}
# new_data_imputed <- impute_preferences(new_data_predictors)
# write_csv(new_data_imputed, file = "clean_data/new_data_imputed.csv")
```

```{r clean my imputed data, warning = FALSE}
new_data_imputed <- read_csv(file = "clean_data/new_data_imputed.csv")

clean_data <- new_data_imputed %>%
  clean_names() %>%
  
  # I exclude the questions where there is no income breakdown.
  
  filter(!is.na(pred50_sw)) %>%
  
  # I use range01() to normalize my predictors to be on a scale 
  # from 0 to 1.
  
  mutate(pred50_norm = range01(pred50_sw),
         pred90_norm = range01(pred90_sw),
         gridlock_norm = range01(gridlock),
         sen_seat_advantage_norm = range01(sen_seat_advantage),
         hs_seat_advantage_norm = range01(hs_seat_advantage))
```

## Correlations

```{r generate correlation matrix}

# I select the predictors relevant for Table 2.

table_2 <- clean_data %>%
  dplyr::select(pred50_norm, pred90_norm, gridlock_norm, 
                sen_seat_advantage_norm, filibuster_proof)

# I use the corstars() function to compute a correlation matrix with stars to
# indicate significant correlations.

table_2_correlation <- corstars(table_2) %>%
  mutate(predictors = c("Median voter", "Affluent voter", 
                        "Gridlock", "Senate seat advantage", "Filibuster-proof")) %>%
  mutate(filibuster_proof = "") %>%
  select(predictors, pred50_norm:sen_seat_advantage_norm, filibuster_proof)

rownames(table_2_correlation) <- NULL

# I format the table using functions from the kableExtra package.

kbl(table_2_correlation, 
    caption = "Correlations among independent variables", 
    col.names = c(" ",
                  "Median voter",
                  "Affluent voter",
                  "Gridlock", 
                  "Senate seat advantage", 
                  "Filibuster-proof"),
    booktabs = T) %>%
    kable_styling(latex_options = c("scale_down")) %>%
    footnote(general = "***p<.001; n = 1779.")
```

## Running models

```{r generate bivariate models}
model_1 <- glm(outcome ~ pred50_norm, 
               family = binomial(link="logit"),
               data = clean_data)

model_2 <- glm(outcome ~ pred90_norm, 
               family = binomial(link="logit"),
               data = clean_data)

model_3 <- glm(outcome ~ gridlock_norm, 
               family = binomial(link="logit"),
               data = clean_data)

model_4 <- glm(outcome ~ sen_seat_advantage_norm, 
               family = binomial(link="logit"),
               data = clean_data)

model_5 <- glm(outcome ~ filibuster_proof, 
               family = binomial(link="logit"),
               data = clean_data)
```

```{r, results = "asis"}
stargazer(model_1, model_2, model_3, model_4, model_5,
          title = "The influence of median voter, affluent voter, gridlock, Senate seat advantage, filibuster-proof majorities on policy outcomes",
          align = TRUE,
          dep.var.labels = c("Policy change"),
          column.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
          covariate.labels = c("Median voter", 
                               "Affluent voter", 
                               "Level of gridlock",
                               "Senate seat advantage",
                               "Filibuster-proof majority"),
          omit.stat=c("LL","ser","f", "n"), 
          no.space=TRUE,
          notes = c("*p<0.1; **p<0.05; ***p<0.01", 
                    "All predictors are scaled to range from 0 to 1. The",
                    "dependent variable is the policy outcome, coded 1 if the", 
                    "proposed policy change took place within four years of the",
                    "survey date and 0 if it did not. These are all bivariate",
                    "logistic regressions. N = 135."),
          notes.align = "l",
          notes.append = FALSE)
```

```{r generate multivariate models for gridlock}
# I run a multivariate model where the preferences of the median voter,
# gridlock, and the interaction between the preferences of the median voter and
# gridlock are predictors of policy change.

model_6 <- glm(outcome ~ pred50_norm + gridlock_norm + pred50_norm*gridlock_norm, 
               family = binomial(link="logit"),
               data = clean_data)

# I run a multivariate model where the preferences of the affluent voter,
# gridlock, and the interaction between the preferences of the affluent voter 
# and gridlock are predictors of policy change.

model_7 <- glm(outcome ~ pred90_norm + gridlock_norm + pred90_norm*gridlock_norm, 
               family = binomial(link="logit"),
               data = clean_data)


# I use invlogit() to convert to predicted probabilities for policy change to
# be adopted. This makes the coefficient more interpretable.

d = coef(model_6)
pred50_norm_avg <- mean(clean_data$pred50_norm)
invlogit(d[1] + d[2]*pred50_norm_avg + d[3]*0.44 + d[4]*pred50_norm_avg*0.44)
invlogit(d[1] + d[2]*pred50_norm_avg + d[3]*0.88 + d[4]*pred50_norm_avg*0.88)

e = coef(model_7)
pred90_norm_avg <- mean(clean_data$pred90_norm)
invlogit(d[1] + d[2]*pred90_norm_avg + d[3]*0.44 + d[4]*pred90_norm_avg*0.44)
invlogit(d[1] + d[2]*pred90_norm_avg + d[3]*0.88 + d[4]*pred90_norm_avg*0.88)
```

```{r, results = "asis"}
stargazer(model_6, model_7,
          title = "The influence of gridlock on governmental responsiveness to the median voter and affluent voter",
          align = TRUE,
          dep.var.labels = c("Policy change"),
          column.labels = c("Model 6", "Model 7"),
          covariate.labels = c("Preferences of median voter", 
                               "Preferences of affluent voter", 
                               "Level of gridlock",
                               "Preferences of median voter*Gridlock",
                               "Preferences of affluent voter*Gridlock"),
          omit.stat=c("LL","ser","f", "n"), 
          no.space=TRUE,
          notes = c("*p<0.1; **p<0.05; ***p<0.01", 
                    "All predictors are scaled to range from 0 to 1. The",
                    "dependent variable is the policy outcome, coded 1 if the", 
                    "proposed policy change took place within four years of the",
                    "survey date and 0 if it did not. These models are all",
                    "multivariate logistic regressions. N = 135."),
          notes.align = "l",
          notes.append = FALSE)
```

```{r generate multivariate models for Senate seat advantage}
# I run a multivariate model where the preferences of the median voter,
# Senate seat advantage, and the interaction between the preferences of the 
# median voter and Senate seat advantage are predictors of policy change.

model_8 <- glm(outcome ~ pred50_norm + sen_seat_advantage_norm + pred50_norm*sen_seat_advantage_norm, 
               family = binomial(link="logit"),
               data = clean_data)

# I run a multivariate model where the preferences of the median voter,
# Senate seat advantage, and the interaction between the preferences of the 
# median voter and Senate seat advantage are predictors of policy change.

model_9 <- glm(outcome ~ pred90_norm + sen_seat_advantage_norm + pred90_norm*sen_seat_advantage_norm, 
               family = binomial(link="logit"),
               data = clean_data)
```

```{r, results = "asis"}
stargazer(model_8, model_9,
          title = "The influence of Senate seat advantage on governmental responsiveness to the median voter and affluent voter",
          align = TRUE,
          dep.var.labels = c("Policy change"),
          column.labels = c("Model 8", "Model 9"),
          covariate.labels = c("Preferences of median voter", 
                               "Preferences of affluent voter", 
                               "Senate seat advantage",
                               "Preferences of median voter*Senate seat advantage",
                               "Preferences of affluent voter*Senate seat advantage"),
          omit.stat=c("LL","ser","f", "n"), 
          no.space=TRUE,
          notes = c("*p<0.1; **p<0.05; ***p<0.01", 
                    "All predictors are scaled to range from 0 to 1. The",
                    "dependent variable is the policy outcome, coded 1 if the", 
                    "proposed policy change took place within four years of the",
                    "survey date and 0 if it did not. These models are all",
                    "multivariate logistic regressions. N = 135."),
          notes.align = "l",
          notes.append = FALSE)
```
```{r generate multivariate models for filibuster proof majorities}
model_10 <- glm(outcome ~ pred50_norm + filibuster_proof + pred50_norm*filibuster_proof, 
               family = binomial(link="logit"),
               data = clean_data)

model_11 <- glm(outcome ~ pred90_norm + filibuster_proof + pred90_norm*filibuster_proof, 
               family = binomial(link="logit"),
               data = clean_data)
```

```{r, results = "asis"}
stargazer(model_10, model_11,
          title = "The influence of filibuster-proof majorities on governmental responsiveness to the median voter and affluent voter",
          align = TRUE,
          dep.var.labels = c("Policy change"),
          column.labels = c("Model 10", "Model 11"),
          covariate.labels = c("Preferences of median voter", 
                               "Preferences of affluent voter", 
                               "Filibuster-proof majority",
                               "Preferences of median voter*Filibuster-proof majority",
                               "Preferences of affluent voter*Filibuster-proof majority"),
          omit.stat=c("LL","ser","f", "n"), 
          no.space=TRUE,
          notes = c("*p<0.1; **p<0.05; ***p<0.01", 
                    "All predictors are scaled to range from 0 to 1. The",
                    "dependent variable is the policy outcome, coded 1 if the", 
                    "proposed policy change took place within four years of the",
                    "survey date and 0 if it did not. These models are all",
                    "multivariate logistic regressions. N = 135."),
          notes.align = "l",
          notes.append = FALSE)
```

More gridlock, less responsiveness to the median voter. 
More gridlock, less responsiveness to the affluent voter.

More senate seat advantage, more responsiveness to median voter. (not significant)
More senate seat advantage, more responsiveness to affluent voter. (not significant)

Filibuster proof, more responsive to median voter (not significant)
Filibuster proof, more responsive to affluent voter (not significant)

## Running analyses



